Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-05-05 doc/paper.tex
updates tables

@@

\begin{table*}[t]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c | c c c c c c | c c c c c c |}
                                &          &      & \multicolumn{6}{|c|}{Semantic Segmentation (mIOU)} & \multicolumn{6}{|c|}{Instance Segmentation (mAP@0.5)}                                                                                                                                                                                                                               \\
                                & overlap  & Scan & 5\%                                                & 10\%                                                  & 20\%                   & 30\%                   & 40\%                   & 100\%                  & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch             & --       & --   & 42.2                                               & 51.09                                                 & 58.23                  & 59.23                  & 62.17                  & 67.43                  & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast       & $>$ 30\% & Pair & 44.79 \textbf{(+2.59)}                             & 55.28 \textbf{(+4.19)}                                & 57.98 (-0.25)          & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            CSC                 & $>$ 30\% & Pair & 42.6 \textbf{(+0.4)}                               & 53.03 \textbf{(+1.94)}                                & 57.28 (-0.95)          & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CSC                 & $>$ 70\% & Pair & 45.44 \textbf{(+3.24)}                             & 50.84 (-0.25)                                         & 59.26 \textbf{(+1.03)} & 59.72 \textbf{(+0.49)} & 62.72 \textbf{(+0.55)} & 68.01 \textbf{(+0.58)} & --                   & --            & --                   & --                   & --          & --                   \\
            CSC                 & --       & Same & 44.09 \textbf{(+1.89)}                             & 50.88 (-0.21)                                         & 56.64 (-1.59)          & 58.9 (-0.33)           & 61.50 (-0.67)          & 67.37 (-0.06)          & --                   & --            & --                   & --                   & --          & --                   \\
            CME \textbf{(Ours)} & --       & Same & 44.04 \textbf{(+1.84)}                             & 52.97 \textbf{(+1.88)}                                & 58.6 \textbf{(+0.37)}  & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table}
    \centering
    \resizebox{0.45\textwidth}{!}{
        \begin{tabular}{ c | c c c c }
                                & min overlap & Same Scan  & Semantic (mIOU)                 & Instance (mAP@0.5)            \\
            \hline
            Scratch             & --          & --         & 65.06                           & 53.0                          \\
            Supervised          & --          & --         & \textbf{70.22} \textbf{(+5.16)} & \textbf{56.2} \textbf{(+3.2)} \\
            \hline
            PointContrast       & 30\%        &            & 66.22 \textbf{(+1.16)}          & 54.8 \textbf{(+1.8)}          \\
            PointContrast       & 70\%        &            & 68.58 \textbf{(+3.52)}          & 55.3 \textbf{(+2.3)}          \\
            PointContrast       &             & \checkmark & 64.97 (-0.09)                   & 56.6 \textbf{(+3.6)}          \\
            CSC                 & 30\%        &            & 68.96 \textbf{(+3.9)}           & 57.8 \textbf{(+4.8)}          \\
            CSC                 & 70\%        &            & \textbf{70.12} \textbf{(+5.06)} & \textbf{58.9} \textbf{(+5.9)} \\
            CSC                 &             & \checkmark & 67.94 \textbf{(+2.88)}          & 57.2 \textbf{(+4.2)}          \\
            DepthContrast       &             & \checkmark & 64.91 (-0.15)                   & 52.3 (-0.7)                   \\
            CME \textbf{(Ours)} &             & \checkmark & 66.48 \textbf{(+1.42)}          & 55.8 \textbf{(+2.8)}          \\
        \end{tabular}
    }
    \caption{S3DIS downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet}
    \label{table:s3disResults}
\end{table}

>>>>

% \subsection{Evaluation Metrics}
% \label{sec:results:metrics}
% \dots

@@

\begin{table*}[t!]
    \centering
    \resizebox{\textwidth}{!}{
        \begin{tabular}{ c | c c | c c c c c c | c c c c c c |}
                                &          &      & \multicolumn{6}{|c|}{Semantic Segmentation (mIOU)} & \multicolumn{6}{|c|}{Instance Segmentation (mAP@0.5)}                                                                                                                                                                                                                               \\
                                & overlap  & Scan & 5\%                                                & 10\%                                                  & 20\%                   & 30\%                   & 40\%                   & 100\%                  & 5\%                  & 10\%          & 20\%                 & 30\%                 & 40\%        & 100\%                \\
            \hline
            Scratch             & --       & --   & 42.2                                               & 51.09                                                 & 58.23                  & 59.23                  & 62.17                  & 67.43                  & 26.9                 & \textbf{31.1} & 40.7                 & 42.2                 & 45.7        & 49.0                 \\
            \hline
            PointContrast       & $>$ 30\% & Pair & 44.79 \textbf{(+2.59)}                             & 55.28 \textbf{(+4.19)}                                & 57.98 (-0.25)          & 58.97 (-0.26)          & 63.17 \textbf{(+1.00)} & 66.88 (-0.55)          & 27.0 \textbf{(+0.1)} & 35.3          & 40.5 (-0.2)          & 43.0 \textbf{(+0.8)} & 43.9 (-1.8) & 49.1 \textbf{(+0.1)} \\
            CSC                 & $>$ 30\% & Pair & 42.6 \textbf{(+0.4)}                               & 53.03 \textbf{(+1.94)}                                & 57.28 (-0.95)          & 62.15 \textbf{(+2.92)} & 65.15 \textbf{(+2.98)} & 67.62 \textbf{(+0.19)} & 29.8 \textbf{(+2.9)} & 35.5          & 41.6 \textbf{(+0.9)} & 42.9 \textbf{(+0.7)} & 44.6 (-1.1) & 49.3 \textbf{(+0.3)} \\
            CSC                 & $>$ 70\% & Pair & 45.44 \textbf{(+3.24)}                             & 50.84 (-0.25)                                         & 59.26 \textbf{(+1.03)} & 59.72 \textbf{(+0.49)} & 62.72 \textbf{(+0.55)} & 68.01 \textbf{(+0.58)} & --                   & --            & --                   & --                   & --          & --                   \\
            CSC                 & --       & Same & 44.09 \textbf{(+1.89)}                             & 50.88 (-0.21)                                         & 56.64 (-1.59)          & 58.9 (-0.33)           & 61.50 (-0.67)          & 67.37 (-0.06)          & --                   & --            & --                   & --                   & --          & --                   \\
            DepthContrast       & --       & Same & 49.27 \textbf{(+7.07)}                             & 54.27 \textbf{(+3.18)}                                & 58.21 (-0.02)          &                        &                        &                        & 24.9 (-2.0)          & 33.8          & 38.2 (-2.5)          & --                   & --          & --                   \\
            CME \textbf{(Ours)} & --       & Same & 44.04 \textbf{(+1.84)}                             & 52.97 \textbf{(+1.88)}                                & 58.6 \textbf{(+0.37)}  & 60.73 \textbf{(+1.5)}  & 63.31 \textbf{(+1.14)} & 67.71 \textbf{(+0.28)} & 25.5 (-1.4)          & 35.5          & 39.1 (-1.6)          & 42.4 \textbf{(+0.2)} & 43.6 (-2.1) & 48.5 (-0.5)          \\
        \end{tabular}
    }
    \caption{Scannet downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet)}
    \label{table:scannetVaryingDataAmount}
\end{table*}

\begin{table}
    \centering
    \resizebox{0.45\textwidth}{!}{
        \begin{tabular}{ c | c c c c }
                                & overlap  & Scan & Semantic (mIOU)                 & Instance (mAP@0.5)            \\
            \hline
            Scratch             & --       & --   & 65.06                           & 53.0                          \\
            Supervised          & --       & --   & \textbf{70.22} \textbf{(+5.16)} & \textbf{56.2} \textbf{(+3.2)} \\
            \hline
            PointContrast       & $>$ 30\% & Pair & 66.22 \textbf{(+1.16)}          & 54.8 \textbf{(+1.8)}          \\
            PointContrast       & $>$ 70\% & Pair & 68.58 \textbf{(+3.52)}          & 55.3 \textbf{(+2.3)}          \\
            PointContrast       &          & Same & 64.97 (-0.09)                   & 56.6 \textbf{(+3.6)}          \\
            CSC                 & $>$ 30\% & Pair & 68.96 \textbf{(+3.9)}           & 57.8 \textbf{(+4.8)}          \\
            CSC                 & $>$ 70\% & Pair & \textbf{70.12} \textbf{(+5.06)} & \textbf{58.9} \textbf{(+5.9)} \\
            CSC                 &          & Same & 67.94 \textbf{(+2.88)}          & 57.2 \textbf{(+4.2)}          \\
            DepthContrast       &          & Same & 64.91 (-0.15)                   & 52.3 (-0.7)                   \\
            CME \textbf{(Ours)} &          & Same & 66.48 \textbf{(+1.42)}          & 55.8 \textbf{(+2.8)}          \\
        \end{tabular}
    }
    \caption{S3DIS downstream semantic (mIOU) and instance (mAP@0.5) segmentation performance using weights pre-trained in Scannet}
    \label{table:s3disResults}
\end{table}

\begin{table}
    \centering
    \resizebox{0.4\textwidth}{!}{
        \begin{tabular}{c | c c c}
                                       & Scannet              & SunRGBD              \\
            \hline
            Scratch                    & 35.2                 & 32.0                 \\
            \hline
            PointContrast              & 36.7 \textbf{(+1.5)} & 34.2 \textbf{(+2.2)} \\
            Contrastive Scene Contexts & 36.1 \textbf{(+0.9)} & 35.1 \textbf{(+3.1)} \\
            DepthContrast              & 33.9 (-1.3)          & 32.9 \textbf{(+0.9)} \\
            CME \textbf{(Ours)}        & 37.7 \textbf{(+2.5)} & 33.1 \textbf{(+1.1)} \\
        \end{tabular}
    }
    \caption{Object Detection using VoteNet  (mAP)}
    \label{table:scannetObjectDetection}
\end{table}
